RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-27 paper/paper7/paper7.tex
contribution

The main \textbf{contribution} of this paper is the development of a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification}).
We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent. 
Within the context of a complex and complete real world running example from the \emph{SBE} domain, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in rectangular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the constraint classification system, to ensure high quality of and trust in (meta)data.

>>>>

We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints of 53 distinct constraint types 
to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
By applying the proposed classification system to several vocabularies to represent both metadata and data, we prove its generality \cite{BoschZapilkoWackerowEckert2015}.

-----

The main \textbf{contribution} of this paper is the development of a system 
\begin{enumerate}
	\item to classify RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary and 
	\item to classify RDF constraint types which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification}).
\end{enumerate}
By defining a huge amount of constraints of different constraint types,   
we apply the proposed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.

We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent. 
Within the context of a complex and complete real world running example from the \emph{SBE} domain, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
how data in rectangular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the constraint classification system, to ensure high quality of and trust in (meta)data.
